Forecasting the 2024 U.S. Presidential Election: Kamala Harris' Projected Victory

### 2024-11-04 paper/paper.qmd
committing changes to paper.qmd

The model was implemented using the **`brms`** package in R, applying a **Beta distribution** with a **logit link function** to accurately model the proportions of support:

>>>>

The model was implemented using the 'brms' package [@brms] in R [@citeR], applying a Beta distribution with a logit link function to accurately model the proportions of support:
